Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Update todo
Test citing

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship.
Footprints from different datasets may be formed at a different level of detail.
Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm (Douglas and Peucker, 1973), to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
In either case The Oriented Minimum Bounding Rectangle (OMBR) is calculated for the two polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coinside with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.

@@

% Wednesday:
% TODO: Merge 2.1, 2.2
% TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: 2.1: Add section refereces to implementation and results of the sub-questions

% Thursday:
% TODO: Verify that citings look correct (compare to other reports)
% TODO: Abstract: Mention that the scientific study is a contribution
% TODO: Main challenge: How to reconstruct a 3D city. Make this more clear in the abstract
% TODO: Introduction (See meeting log for suggestions)
% TODO: Introduction, picture of a virtual city

@@

% After next meeting with Chris
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Edge distance algorithm, outline, algorithm + picture
% TODO: Spell check
% TODO: Go over report one final time
% TODO: Swedish abstract

@@

\bibitem{douglas-peucker-73}
Douglas, D.H. \& Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.

>>>>

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship.
Footprints from different datasets may be formed at a different level of detail.
Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm \cite{douglas-73}, to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
In either case The Oriented Minimum Bounding Rectangle (OMBR) is calculated for the two polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coinside with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.

@@

% Thursday:
% TODO: Reference labels
% TODO: Fix citings like they appear in the example thesis
% TODO: Abstract: Mention that the scientific study is a contribution

% TODO: Introduction (See meeting log for suggestions)
    % TODO: Introduction, picture of a virtual city
    % TODO: Main challenge: How to reconstruct a 3D city. Make this more clear in the abstract
    % TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

@@

% After next meeting with Chris
% TODO: Spell check
% TODO: Go over report one final time
% TODO: Swedish abstract

@@

\bibitem{douglas-73}
Douglas, D.H. \& Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.
